Subglacial and subaerial fluvial sediment transport capacity respond differently to water discharge variations

### 2024-03-22 Delaneyetal2024.tex
to daniel

Results from  both \alpine{} and \icesheet{} scenarios show that the variability in subglacial  decreases with aggregations longer than approximately 1--5 days (Figure~\ref{fig:multi_run}).
Yet, substantial differences in the variability between the model outputs for subglacial and subaerial cases persist in periods of up to $15$ days, after which seasonal variations might be conflated.
Note that the timing of peak sediment transport conditions still occurs across these periods, and they are are thus not captured in aggregating water discharge over longer periods (Figure~\ref{fig:model_outs}).

@@

Sediment transport capacity in subglacial channels responds more rapidly to changes in water discharge compared to their subaerial counterparts \cite{alley1997}.
In subglacial R\"othlisberger channels in steady state with water discharge, the width-integrated shear stress response to water discharge is $ w_g\,\tau_{g}\, \propto\,  Q^{\sim\frac{4}{5}}$ (Table\,\ref{tab:eqs1}).
However, subglacial channels rarely operate in a steady state \cite<e.g.>{gimbert2016}.
For sufficiently short periods, channel width and wetted area are fixed in the subglacial system (akin to pipe flow) so that the response of width-integrated shear stress is $w_g\, \tau_{g}\, \propto\,  Q^{2}$ (Table\,\ref{tab:eqs1}).
\ref{sect:scaling} provides a complete description of sediment transport capacity in different drainage conditions.
Note that in pipe flow conditions, maximum sediment transport would coincide with peak water discharge and a co-varying relationship with water discharge would occur, unlike with the evolving channel size here (Section~\ref{sect:sub_mode}; Figure \ref{fig:model_outs} and \ref{fig:Qw_vari}). 
Similar adjustments in channel shape occur in subaerial channels \cite{phillips2016}, albeit at timescales longer than hours to days in subglacial channels.

>>>>

Results from  both \alpine{} and \icesheet{} scenarios show that the variability in subglacial  decreases with aggregations longer than approximately 1--5 days (Figure~\ref{fig:multi_run}).
Yet, substantial differences in the variability between the model outputs for subglacial and subaerial cases persist in periods of up to $15$ days, longer than which seasonal variations might be conflated.
Note that the timing of peak sediment transport conditions still occurs across these periods, and they are are thus not captured in aggregating water discharge over longer periods (Figure~\ref{fig:model_outs}).

@@

Sediment transport capacity in subglacial channels responds more rapidly to changes in water discharge compared to their subaerial counterparts \cite{alley1997}.
In subglacial R\"othlisberger channels in steady state with water discharge, the width-integrated shear stress response to water discharge is $ w_g\,\tau_{g}\, \propto\,  Q^{\sim\frac{4}{5}}$ (Table\,\ref{tab:eqs1}).
However, subglacial channels rarely operate in a steady state \cite<e.g.>{gimbert2016}.
For sufficiently short periods, channel width and wetted area are fixed in the subglacial system (akin to pipe flow) so that the response of width-integrated shear stress is $w_g\, \tau_{g}\, \propto\,  Q^{2}$ (Table\,\ref{tab:eqs1}).
\ref{sect:scaling} provides a complete description of sediment transport capacity in different drainage conditions.
Note that in pipe flow conditions, maximum sediment transport would coincide with peak water discharge and a co-varying relationship with water discharge would occur, unlike with the evolving channel size here where a disparate relationship with water discharge occurs (Section~\ref{sect:sub_mode}; Figure \ref{fig:model_outs} and \ref{fig:Qw_vari}). 
Similar adjustments in channel shape occur in subaerial channels \cite{phillips2016}, albeit at timescales longer than hours to days in subglacial channels.
